---
title: "cardknower ETL experimentation"
output: html_notebook
---

## notes on differences from deckdater

-   Single-use instead of self-updating cron job pipeline here

    -   Why: convenience/limitations/proof of concept, not a good fit
        for intended temp host now

-   May concede to mortifying ordeal of denormalization in cases where
    loading in would be predictably denormalizing anyway? Ugh.

    -   Relatedly: use SQLite for project convenience/simplicity's sake

-   *Do* want detailed mechanical information

-   Do *not* currently need individual users/concept of user or
    deck/core dating system

    -   May add sample decks to test pretty table rendering once I'm
        looking for things to do though

-   Primary goal is "look how many fun facts I can visualize"

    -   Secondary goal is "JC look. JC. JC look frontend go brr"
    -   Tertiary goal is "same as above but 'analytics go brr' for Greg
        and Dr. Ben instead"
    -   Quaternary goal is "be more responsible about writing discrete
        packages, instead of being a horse's ass"
    -   Quintenary(?) goal is "experiment with more geoms" but it's the
        lowest priority because I don't actually know if I will need any
        geoms I don't already know anyway

-   This document is allowed to be Like This because it's the one that
    only runs for setup once.

## think of packages I want on hand

```{r}
install.packages("tools") #may or may not need...?
install.packages("rlang") #do I need rlang...?
install.packages("devtools")
install.packages("roxygen")
install.packages("DBI")
install.packages("RSQLite")
install.packages("rvest") #get comprehensive rules
install.packages("RcppSimdJson") #faster than jsonlite
install.packages("data.table") #I insist 
install.packages("shiny") #add golem later?
install.packages("magrittr") #pipe insurance
install.packages("forcats") #be responsible herding cats
install.packages("purrr") #may not need, we'll see
install.packages("lubridate") #ditto

#ggplot and friends
install.packages("ggplot2") 
##...check for redundancy in practice later 
install.packages("hrbrthemes") 
install.packages("ggthemes") 
  #someday I will find aesthetics I like
install.packages("gganimate")
install.packages("ggforce")
install.packages("ggbeeswarm")
install.packages("ggbump")
install.packages("ggalluvial")
install.packages("ggExtra") #marginal plots 
install.packages("ggpattern") #use card art as backgrounds
install.packages("ggblur") #Cyrus's Visual Acuity Simulator
```

## initial database setup

```{sql}

```

### rote lookup tables go here

```{sql}

```

## scrape comprehensive rules

```{r}

```

### keyword-related lookup tables

```{r}

```

## fetch from API endpoint and save to disk

```{r}

```

### fetch images for fun and save

```{r}

```

## load and save sets data

```{r}

```

### save as raw in db

```{r}

```

## load main card data for wrangling

```{r}

```

### save as raw in db

```{r}

```

## load translation data for wrangling

```{r}

```

### save as raw in db

```{r}

```

## write lang lookup table

```{r}

```

## database transforms from here

```{r}

```

## note

In theory this is the point where I should move on to another document and in practice whether I start experimenting with what analytics batches should look like here or elsewhere is inevitably going to depend just on whether we've hit enough lines of code that it's hard to scroll up and down yet or not.